---
title: "Vegetable Pricing White Paper"
author: "Lucas Hilsbos"
date: "3/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We read in CSV price data from the USDA Agricultural Marketing Serive for the terminal market price of apples. The data spans 1998 to present - all years available in the AMS's tool. We will review the complete data before seperating the data into several data frames for analysis
```{r}
data_1 <- read.csv('1998_2022_100_Tray_Apples.csv')
head(data_1)
summary(data_1)
```

```{r}
#Converting Date values to numeric

#install.packages("tidyverse")
library("tidyverse")
library("lubridate")
help("lubridate")

data_1$Date<-as.Date(data_1$Date, format = "%Y/%m/%d")
data_1$Date<-julian(data_1$Date)

head(data_1)
summary(data_1)
class(data_1$Date)
```


Next we will look at a few line graphs showing price over time for all apples meeting the specifications mentioned above.

```{r}
plot(High.Price~Date, xlab = "Date", ylab = "High Terminal Market Price", main = "US Fancy Wholesale apple Pricing", data = data_1)
```

